Resonation Elicits Diffusion: \\Modelling Subjectivity for Retweeting Analysis

### 2014-01-25 retweet_aaai.tex
20140125

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{multirow}
\newtheorem{definition}{Definition}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Resonation Elicits Diffusion: \\Modelling Subjectivity for Retweeting Analysis}
%\author{AAAI Press\\
%Association for the Advancement of Artificial Intelligence\\
%2275 East Bayshore Road, Suite 160\\
%Palo Alto, California 94303\\
%}
\maketitle
\begin{abstract}
\begin{quote}
Retweeting is the core mechanism of information diffusion on Twitter. User modelling has been proved effective in  retweeting behavior analysis, however none studies have investigated the subjectivity of users. 
In this paper, we propose a subjective model by combining both topics of interest and opinions to model users, and demonstrate that a user is more likely to retweet a message because of subjective similarity. 
We define a novel weighting function to measure the subjective similarity. 
By means of ANOVA test, the subjective similarity is verified to be correlated with  retweeting behavior;  
we compare our model with other content-based models in retweeting prediction and results show that our model  outperforms other models for predicting retweeting behavior; 
when combining with other factors, subjective similarities give significant improvement over a off-the-shelf predicting model.
\end{quote}
\end{abstract}

\section{Introduction}
\label{introduction}
\noindent Microblogging has become a center of attention in the area of social networking due to the amount of users it has attracted and the volume of messages it produces daily. 
Microblogging services such as Twitter appear to play an important role in the process of information dissemination on the Internet, making it possible for messages to spread virally in a matter of minutes. 
Retweeting convention and complex network of Twitter provide an unprecedented mechanism for the spread of information despite the restricted length of a single message(tweet) \cite{Jenders:2013APV}. 
Actually almost a quarter of the tweets are retweeted from others \cite{conf/cikm/YangGCTLZS10}. 
Understanding how retweeting behavior works can help explaining information dissemination on Twitter.

Studies have tried to find factors that influence whether a tweet will be retweeted \cite{Boyd2010,Kwak:2010TSN,Suh2010}. 
Users receive thousands of tweets on different topics every day, whether a tweet will be retweeted will depend on the subjective choice of users. 
From the point of a user, retweeting is a process that includes reading the tweet, estimating the content and deciding to share. The crucial part is to estimate whether a tweet contains information interesting to the user who might find it worthy to be shared.  
Therefore modelling the motivation of users provides an important perspective for retweeting behavior analysis. 
This research is motivated by a desire to understand what drives users of social networks to disseminate information they come across.

Previous studies on retweeting behavior have shown that an enriched user model gives coherent and consistent explanation for retweeting motivation \cite{conf/icwsm/MacskassyM11,conf/wsdm/FengW13}. 
Specifically, researchers have tried to model users from four types of information:
profile features (``\textbf{Who you are}"), tweeting behavior (``\textbf{How you tweet}"), linguistic content (``\textbf{What you tweet}") and social network (``\textbf{Who you tweet}") \cite{Pennacchiotti:icwsm11}. 
Subjective initiative nature of human determines that his behavior pattern is subjectivity driven. 
According to theory of Biased Assimilation, people are prone to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
Therefore, we can understand the underlying reason why a user retweet a message by modelling the subjectivity of the user.

Twitter has become a platform where different opinions are presented and exchanged by allowing users publish subjective messages on topics they are interested in. 
Therefore subjectivity of a user is encoded in the millions of User-Generated Content(UGC) on Twitter. 
In this study we explore the big text data with state-of-the-art Natural Language Processing techniques to model the subjectivity of users, and investigate whether the subjective model could benefit the retweeting behavior analysis. 
Intuitively, we put forwards that subjectivity can be represented as topics and opinions articulated in the tweets generated by users on Twitter. 
And the probabilty a user retweets a message could be evaluated by measuring the subjective similarity between the tweet and the subjective model of the user.

@@

Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historic behaviors and remarks \cite{Engbert2007}. 
Linguists define the subjectivity of language as speakers always show their perspectives, attitudes and sentiments to events, people, topics, and entities in their languistic content \cite{stein2005subjectivity}. 
How to computationally model subjectivity of a user is still a challenging problem for many applications. 
The advent of online social networking such as Twitter has given a new layout to the challenge.  
Twitter allows users to show their personal subjectivity by publishing short messages, which give researchers resources to model the subjectivity of users.
First of all, we give an formal definition for subjective model under context of Twitter.

@@

Let $G=\left( V,E \right) $ denotes a social network, where $ V $ is a set of users on Twitter, and $ E\subset V\times V $ is a set of directed relationships between users. For each user $ u \in V $, there is a tweets collection $ M_{u} $ denotes his message history. We assume there is a topic space $ T $ containing all topics they talk about, and a sentiment valence space $ O $ for evaluating their opinions towards these topics. 
For the ``subjectivity'' of a user $ u $, we refer to both topics of interest and opinions articulated in his tweets collection $ M_{u} $.  
\begin{definition}[Subjective Model]
The subjective model $ P \left( u \right) $ of a user $u \in V $, is the combination of a set of topics $\left\lbrace  t_{i} \left( i \in \lbrace1 \cdots n \rbrace \right)  \right\rbrace $ the user talks about in a topic space $T$ and the user's opinion $o_{i}$ towards each topic $ t_{i} $. 
\begin{equation}
\label{usermodel}
P \left( u \right) = \lbrace \left( t_{i}, w_{u} \left( t_{i} \right), d_{u,t_{i}} \left( o_{i} \right) \right) \,\vert  t_{i} \in T, \, o_{i} \in O \rbrace
\end{equation}
where:
\begin{itemize}
\item with respect to the given user $ u $,  for each topic $t_{i} \in T$, its  weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, with $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
\item opinion of the user towards topic $t_{i}$ is modeled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
\end{itemize}
\end{definition}
The definition of subjective model given above is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from message history of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$

\subsection{Establishment of Subjective Model}
\label{establishment}
According to the definition, subjective model of a user can be represented as two distributions: the topic distribution and the sentiment distribution for each topic. 
With state-of-the-art topic model and sentiment analysis techniques, we can establish subjective model by finding topics and opinions simultaneously. 
\subsubsection{Topic Analysis}
\label{topic}
Previous studies have tried to identify topics by finding key words \cite{Chen:2010STE}, extracting  entities \cite{Abel:2011AUM} or linking tweets to external knowledge categories \cite{conf/icwsm/MacskassyM11}. Recent works show that topic models such as \textbf{Latent Dirichlet Allocation (LDA)} model \cite{blei2003latent} have been efficient ways to characterize latent topics of large volume corpus.  
Topics of LDA are broader in concept, since a single topic consists of the whole collection of related words, so we adopt the LDA topic model for topic analysis.  
Topic analysis for all users in a global network on Twitter is a nontrivial task. 
There are millions of users and billions of tweets associcated with these users, and the effectiveness and efficiency of topic model is a big problem.
However, the ``following'' relationship on Twitter is a strong indicator of a phenomenon called ``homophily", which has been observed in many social networks \cite{mcpherson2001birds}.
Homophily implies that a user follows another user because of sharing common topics of interest. 
According to the principle of homophily, we put forwards the concept of \textbf{Local Topic Space}: 
\begin{definition}[Local Topic Space]
\label{local}
Let $G=\left( V,E \right) $ denotes a global social network, for a user $ u \in V $, we use $ G_{u}^{\tau} \subseteq G$ 
to denote $ u $'s $ \tau $-ego network, where $ \tau $ -ego network means a subnetwork formed by $ u $'s $ \tau $-hop 
friends in the network $ G $, and $ \tau \geqslant 1 $ is a tunable integer parameter to control the scale of the ego network. 
In the $ \tau $-ego network of user $ u $, all users concentrate on a few topics derived from the content generated by them, and these topics form a local topic space $ T_{u} $.
\end{definition}
The relatively tiny size and topic homophily of ego network lower the impact of data sparsity and degrade the complexity of calculation.

Therefore we adopt a user-level LDA model to find latent topics in Local Topic Space by aggregating all tweets generated by a user into a single document just as \cite{Hong:2010EST}. 
The result of LDA produces two multinomial distributions, with distribution $ \theta_{u} $ representing the probability distribution of a user over each topic, and distribution $ \beta_{k} $ representing the probability distribution of a topic over whole vocabulary used by all users in ego network.

@@

Users often express opinions towards topics of interest by publishing topic-related tweets. 
Sentiment analysis or opinion mining is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}. Opinions are regulated as sequential discrete values to represent sentiment strength(for example: 0 stands for negtive and 1 for positive). Recently, researchers began to pay more and more attention to social media such as Twitter \cite{Thelwall:2010SSS,Thelwall:2012SSD,Hu:2013www} and provide effective sentiment analysis tools.

SentiStrength package has been built especially to cope with sentiment analysis in short informal text of social media \cite{Thelwall:2010SSS}. 
It combines lexicon-based approaches with sophisticated linguistic rules adapted to social media, which is suitable for analyzing sentiment of tweets.
SentiStrength assigns two values to each tweet standing for sentiment strengths: a positive and a negative sentiment measurement, with $ \left[ -5,-1 \right]  $ denoting negative and $ \left[ 1,5 \right]  $ denoting positive sentiment strength.
Sentiment assigned by SentiStrength is a fine-grained strength, which can catch fine opinion distributions in a user's subjective model.  
For the convenience of distribution calculation, we map the output of SentiStrength to single-scaled sentiment valence space $ \left[ 0, 8 \right] $ as follows:
\begin{equation}
\label{opinionmap}
o= \left\{ 
\begin{array}{lll}
{p+3} & if \vert p \vert > \vert n \vert \\
{n+5} & \text{if } \vert n \vert > \vert p \vert \\
{4}  & \text{if } \vert p \vert = \vert n \vert
\end{array}
\right.
\end{equation}
Where $ p $ denotes the positive setiment strength and $ n $ denotes negative sentment strength.
In the sentiment valence space, value 4 indicates neutral sentiment, while values above 4 indicate positive sentiment and values below 4 indicate negative sentiment.

@@

As Definition~\ref{local} describes, for a user $ u $ in a global netwotk, we can extract a $ \tau $-ego network $ G_{u}=\left( U,E_{u} \right)  $. 
And the subjective model of each user $ u \in G_{u} $ can be concreted within the ego network. 
We denote tweets set published by a user $ u $ as $ M_{u}=\left\lbrace m_{i} \vert i \in \left[ 1, \cdots, N \right]  \right\rbrace$. All tweets in $ M_{u} $ is concatenated to a single document $ d_{u} $ to construct Local Topic Space $ T_{u}=\left\lbrace t_{i} \vert i=1, \cdots, K \right\rbrace $ with LDA topic model.
The topic model is built with parameter $ \theta_{u} $\ representing the distribution of user $ u $ over topics he talks about, and parameter $ \beta_{k} $ represents the distribution of each topic over the vocabulary of all tweets. SentiStrength is applied to each tweet $ m $ in collection $ M_{u} $ and outputs sentiment strength $ s_{m} $ for tweet $ m $. 
Subjective model of user $ u $ is built the  as follows:
\begin{itemize}
\item Firstly, for user $ u $, the corresponding $ \theta_{u} $ can be regarded as his topic distribution in the Local Topic Space $ T_{u} $, and topics he cares about are $ Z_{u}= \left\lbrace z \vert p\left( z \vert \theta_{u}\left( z \right)  \right)>0 \right\rbrace $.
\item Secondly, in order to identify the target of opinion in each tweet, the topic model is applied to each tweet $ m $ to find topics it talks about, which are $ Z_{m} =\left\lbrace z_{m} \vert p\left( z_{m} \vert \theta, \beta, Z_{u} \right)>0 \right\rbrace $.
\item Thirdly, the opinion distribution of user $ u $ towards topic $ t \in Z_{u} $ could be calculated as: 
\begin{equation}
\label{opinionall}
d_{u,t}\left( o \right) = \left\lbrace \dfrac{N_{o}}{\sum_{o \in O} N_{o}} \vert O=\left[ 0, \cdots, 8 \right] \right\rbrace 
\end{equation}
where $ N_{o} $ is the number of times user $ u $ expresses an opinion towards topic $ t $ with sentiment strength $ o $, which could be calculated as:
\begin{equation}
\label{opinion1}
N_{o}=\sum_{m \in Mu} I\left( s_{m} \right) , \text{ if } s_{m}=o \& t \in Z_{m}
\end{equation}
\begin{equation}
\label{opinion2}
I\left( s_{m} \right)=\left\{
\begin{array}{ll}
{1} & \text{if } s_{m}=o \& t \in Z_{m}\\
{0} & \text{else}
\end{array}
\right.
\end{equation}
where $ s_{m} $ denotes the sentiment strength of tweet $ m $. For simplicity, we assume the sentiment of tweet $ m $ is related to every topic it talks about in $ Z_{m} $.
\end{itemize}

@@

Many factors have been proved to influence retweeting behavior \cite{Suh2010,conf/icwsm/MacskassyM11,Comarela:2012UFA}, however few researches have investigated the subjective motivation of a user to retweet a message. 
Therefore we will study whether subjective model can help understand underlying reasons of a user's retweeting behavior.
Apart from the context constraints, a tweet is more likely to be retweeted by subjective users who find it worth to. 
Therefore, we are not interested in modelling the tweet by itself as other researches \cite{Naveed:2011SMC,2011:NaveedGKC,conf/icwsm/PfitznerGS12}, but how the tweet resonate with the users who might want to disseminate it. 
We assume the motivation of a user to retweet a message lies in that the user considers only the tweet content arousing his resonation without context perturbation. 
If a tweet is published, all followers of its author will receive it in time, and followers are likely to retweet it if they find it worthwhile. 
Under such assumption, we investigate the problem in 1-ego network for the author of target tweet. 
The relation between tweet, author and followers can be illustrated as Figure~\ref{fig1}.
\begin{figure}[htb]
%\setlength{\belowcaptionskip}{-0.2cm} 
\centering
\includegraphics[width=2.1in,height=2.0in]{ego.pdf}
%\vspace{-4em}
\caption{Illustration of relations between tweet, author and followers. Author is denoted as $ u_{a} $, tweet as $ m $, followers as $ f_{i} $ and tweets of follower $ f_{i} $ as $ m_{i} $. An directed edge $ \left( f_{i},u_{a} \right)  $ means that $ f_{i} $ is exposed to the messages published by $ u_{a} $.}
\label{fig1}
\end{figure}

@@

Retweeting analysis problem can be formulated as follows:
For each target tweet $ m $, let $ F $ denotes the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denotes   tweets the user has published. 
For each follower $ u_{f} \in F $, we can define a quadruple $ <u_{f}, u_{a}, m, r_{f}>  $: 
\begin{itemize}
\item $ r_{f} $ is a binary label indicating whether $ m $ is retweeted by $ u_{f} $.
\item Firstly our work focuses on building subjective model $ P\left( u \right)  $ for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace $ in the ego network with all tweets collections $ M=\left\lbrace M_{u} | u \in F \cup \left\lbrace u_{a} \right\rbrace  \right\rbrace  $.
\item Then we investigate the relation between the subjectivity of a user and his retweeting behavior to predict $ r_{f} $ by calculating subjective similarities between tweet $ m $, its author $ u_{a} $ and follower $ u_{f} $. 
\end{itemize}

@@

In order o understand the underlying reasons why a user retweet a message, we try to simulate the subjective decision-making procedure by investigating the relationship among a tweets and subjective models of its author and followers. 
We assume that if a tweet and the subjective models of a user are similar enough in terms of topics and opinions, the user will have a very high probability to retweet the tweet. 
We call this phenomenon as ``resonation'', and assume resonation between tweets and users will elicit retweeting behavior.
With subjective models built for users, we can define a similarity measurement to quantify the resonation among them.

@@

Topic distribution of a tweet can be inferenced by applying topic model estimated from the tweets collections of users.
The topic similarity between tweet and user can be calculated with methods such as the cosine distance \cite{cha2007comprehensive} or the Jensen-Shannon Divergence \cite{weng2010twitterrank} with satisfactory results.
In our research, we adopt cosine distance to measure the topic similarity, which is defined as:
\begin{equation}
sim_{topic}=\dfrac{\theta_{m} \cdot \theta_{u}}{\parallel \theta_{m} \parallel \parallel \theta_{u} \parallel}
\end{equation}
where $ \theta_{u}$ denotes topic distribution of user $ u $ and $\theta_{m}$ denotes topic distribution of tweet $ m $.

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{multirow}
\newtheorem{definition}{Definition}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Insert Your Title Here)
/Author (Put All Your Authors Here, Separated by Commas)}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Resonation Elicits Diffusion: \\Modelling Subjectivity for Retweeting Analysis}
%\author{AAAI Press\\
%Association for the Advancement of Artificial Intelligence\\
%2275 East Bayshore Road, Suite 160\\
%Palo Alto, California 94303\\
%}
\maketitle
\begin{abstract}
\begin{quote}
Retweeting is one of the key mechanisms of information diffusion on Twitter. User modelling has been proved to be effective in retweeting behavior analysis. However no studies have investigated the subjectivity of users. 
In this paper, we propose a novel subjective model by combining both topics of interest and opinions to model users, and demonstrate that a user is more likely to retweet a message because of subjective similarity. 
We define a novel weighting function to measure the subjective similarity. 
By means of ANOVA test, the subjective similarity is verified to be correlated with retweeting behavior;  
we compare our model with other content-based models in retweeting prediction and the comparison results show that our model outperforms other models for predicting retweeting behavior; 
when combining with other factors, subjective similarities give significant improvement over a off-the-shelf predicting model.
\end{quote}
\end{abstract}

\section{Introduction}
\label{introduction}
\noindent Microblogging has become a center of attention in the area of social networking due to the amount of users it has attracted and the volume of messages it produces daily. 
Microblogging services such as Twitter appear to play an important role in the process of information dissemination on the Internet, making it possible for messages to spread virally in a matter of minutes. 
Retweeting convention and complex network of Twitter provide an unprecedented mechanism for the spread of information despite the restricted length of a single message(tweet). 
Actually almost a quarter of the tweets are retweeted from others \cite{conf/cikm/YangGCTLZS10}. 
Understanding how retweeting behavior works can help explaining information dissemination on Twitter.

Existing studies try to find factors that whether a tweet will be retweeted \cite{Boyd2010,Kwak:2010TSN,Suh2010}. 
Users receive thousands of tweets on different topics every day, however whether a tweet will be retweeted will depend on the subjective choice of users. 
From the point of a user, retweeting is a process that includes reading the tweet, evaluating the content and deciding whether to share. The crucial part is to evaluate whether a tweet contains information interesting to the user who might find that it is worthy to be shared.  
Therefore modelling the motivation of users provides an important perspective for retweeting behavior analysis. 
This research is motivated by a desire to understand what drives users of social networks to disseminate information they come across.

Previous studies on retweeting analysis have shown that an enriched user model gives coherent and consistent explanation for retweeting motivation \cite{conf/icwsm/MacskassyM11,conf/wsdm/FengW13}. 
Specifically, researchers have tried to model users from four types of information:
profile features (``\textbf{Who you are}"), tweeting behavior (``\textbf{How you tweet}"), linguistic content (``\textbf{What you tweet}") and social network (``\textbf{Who you tweet}") \cite{Pennacchiotti:icwsm11}. 
The subjective initiative nature of human determines that his behavior pattern is subjectivity driven. 
According to theory of \textbf{Biased Assimilation}, people tend to choose and disseminate information according to their own biased subjectivity \cite{Hyman2000}. 
Therefore, we can understand the underlying reason why a user retweets a message by modelling the subjectivity of the user.

Twitter has become a platform where different opinions are presented and exchanged by allowing users publish subjective messages on topics they are interested in. 
Therefore, the subjectivity of a user is encoded in the millions of User-Generated Content(UGC) on Twitter. 
In this study we explore the big text data with state-of-the-art Natural Language Processing techniques to model the subjectivity of users, and investigate whether the subjective model can benefit the retweeting behavior analysis. 
Intuitively, we put forwards that subjectivity can be represented as topics and opinions articulated in the tweets generated by users. 
Also the probability that a user retweets a message could be evaluated by measuring the subjective similarity between the tweet and the subjective model of the user.

@@

Subjectivity has been extensively studied by psychologists to characterize the personality of a person based on his historic behaviors and remarks \cite{Engbert2007}. 
Linguists define the subjectivity of language as speakers always show their perspectives, attitudes and sentiments to events, people, topics, and entities in their linguistic contents \cite{stein2005subjectivity}. 
How to computationally model subjectivity of a user is still a challenging problem for many applications. 
The advent of online social networking such as Twitter has given a new layout to the challenge.  
Twitter allows users to show their personal subjectivity by publishing short messages, which give researchers resources to model the subjectivity of users.
First of all, we give a formal definition of the subjective model under the context of Twitter.

@@

Let $G=\left( V,E \right) $ denotes a social network, where $ V $ is a set of users on Twitter, and $ E\subset V\times V $ is a set of directed relationships between users. For each user $ u \in V $, there is a tweets collection $ M_{u} $ denotes his message history. We assume there is a topic space $ T $ containing all topics they talk about, and a sentiment valence space $ O $ for evaluating their opinions towards these topics. 
For the ``subjectivity'' of a user $ u $, we refer to both topics of interest and opinions articulated in his tweets collection $ M_{u} $.  
\begin{definition}[Subjective Model]
The subjective model $ P \left( u \right) $ of a user $u \in V $, is the combination of a set of topics $\left\lbrace  t_{i} \left( i \in \lbrace1 \cdots n \rbrace \right)  \right\rbrace $ the user talks about in a topic space $T$ and the user's opinion $o_{i}$ towards each topic $ t_{i} $. 
\begin{equation}
\label{usermodel}
P \left( u \right) = \lbrace \left( t_{i}, w_{u} \left( t_{i} \right), d_{u,t_{i}} \left( o_{i} \right) \right) \,\vert  t_{i} \in T, \, o_{i} \in O \rbrace
\end{equation}
where:
\begin{itemize}
\item with respect to the given user $ u $,  for each topic $t_{i} \in T$, its  weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, with $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
\item opinion of the user towards topic $t_{i}$ is modeled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
\end{itemize}
\end{definition}
Figure~\ref{fig0} is a visualized subjective model of a user. 
\begin{figure}[htb]
%\centering
\includegraphics[width=3.8in,height=2.5in]{fig1.pdf}
\caption{The left subgraph denotes two topics a user tweets about with weights $ \left( w_{u}\left( t_{23} \right)=0.43, w_{u}\left( t_{86} \right)=0.57\right)  $. the right subgraph denotes opinions towards two topics: for topic 23, $ ( d_{u,t_{23}} \left( o_{2} \right)=0.1, d_{u,t_{23}} \left( o_{4} \right)=0.5,d_{u,t_{23}} \left( o_{5} \right)=0.3,d_{u,t_{23}} \left( o_{6} \right)=0.1) $; for topic 86, $ \left( d_{u,t_{86}} \left( o_{4} \right)=0.66, d_{u,t_{86}} \left( o_{5} \right)=0.34 \right) $.}
\label{fig0}
\end{figure}

The definition of a subjective model given above is in an abstract form by using latent concepts of topics and opinions,  which need to be derived from the message histories of all users $ M=\lbrace M_{u}\vert u \in V\rbrace$

\subsection{Establishment of Subjective Model}
\label{establishment}
According to the definition, a subjective model of a user can be represented as two distributions: the topic distribution and the sentiment distribution for each topic. 
With the state-of-the-art topic model and sentiment analysis techniques, we can establish a subjective model by finding topics and opinions simultaneously. 
\subsubsection{Topic Analysis}
\label{topic}
Previous studies have tried to identify topics by finding key words \cite{Chen:2010STE}, extracting  entities \cite{Abel:2011AUM} or linking tweets to external knowledge categories \cite{conf/icwsm/MacskassyM11}. Recent works show that topic models such as \textbf{Latent Dirichlet Allocation (LDA)} model \cite{blei2003latent} have been efficient ways to characterize latent topics of a large volume corpus.  
Topics of LDA are broader in concept, since a single topic consists of the whole collection of related words, so we adopt the LDA topic model for topic analysis.  
Topic analysis for all users in a global network on Twitter is a nontrivial task. 
There are millions of users and billions of tweets associated with these users, and the effectiveness and efficiency of the topic model is a big problem.
However, the ``following'' relationship on Twitter is a strong indicator of a phenomenon called ``homophily'', which has been observed in many social networks \cite{mcpherson2001birds}.
Homophily implies that a user follows another user because of sharing common topics of interest. 
According to the principle of homophily, we put forwards the concept of \textbf{Local Topic Space}: 
\begin{definition}[Local Topic Space]
\label{local}
Let $G=\left( V,E \right) $ denotes a global social network, for a user $ u \in V $, we use $ G_{u}^{\tau} \subseteq G$ 
to denote $ u $'s $ \tau $-ego network, where $ \tau $ -ego network means a subnetwork formed by $ u $'s $ \tau $-hop 
friends in the network $ G $, and $ \tau \geqslant 1 $ is a tunable integer parameter to control the scale of the ego network. 
In the $ \tau $-ego network of user $ u $, all users concentrate on a few topics derived from the content generated by them, and these topics form a local topic space $ T_{u} $.
\end{definition}
The relatively tiny size and topic homophily of an ego network lower the impact of data sparsity and degrade the complexity of calculation.

Therefore we adopt a user-level LDA model to find latent topics in a Local Topic Space by aggregating all tweets generated by a user into a single document just as \cite{Hong:2010EST}. 
The result of LDA produces two multinomial distributions, with distribution $ \theta_{u} $ representing the probability distribution of a user over each topic, and distribution $ \beta_{k} $ representing the probability distribution of a topic over whole vocabulary used by all users in an ego network.

@@

Users often express opinions towards topics of interest by publishing topic-related tweets. 
Sentiment analysis or opinion mining is formally defined as the computational study of sentiments and opinions about topics expressed in a text \cite{liu2012sentiment}. Opinions are regulated as sequential discrete values to represent sentiment strength (for example: 0 stands for negative and 1 for positive). Recently, researchers began to pay more and more attention to social media such as Twitter \cite{Thelwall:2010SSS,Thelwall:2012SSD,Hu:2013www} and provide effective sentiment analysis tools.

The SentiStrength package has been built especially to cope with sentiment analysis in short informal text in social media \cite{Thelwall:2010SSS}. 
It combines lexicon-based approaches with sophisticated linguistic rules adapted to social media, which is suitable for analyzing sentiment of tweets.
SentiStrength assigns two values to each tweet standing for sentiment strengths: a positive and a negative sentiment measurement, with $ \left[ -5,-1 \right]  $ denoting negative and $ \left[ 1,5 \right]  $ denoting positive sentiment strength.
Sentiment assigned by SentiStrength is a fine-grained strength, which can catch fine opinion distributions in a user's subjective model.  
For the convenience of distribution calculation, we map the output of SentiStrength to single-scaled sentiment valence space $ \left[ 0, 8 \right] $ as follows:
\begin{equation}
\label{opinionmap}
o= \left\{ 
\begin{array}{lll}
{p+3} & if \vert p \vert > \vert n \vert \\
{n+5} & \text{if } \vert n \vert > \vert p \vert \\
{4}  & \text{if } \vert p \vert = \vert n \vert
\end{array}
\right.
\end{equation}
where $ p $ denotes the positive sentiment strength and $ n $ denotes negative sentiment strength.
In the sentiment valence space, value 4 indicates neutral sentiment, while values above 4 indicate positive sentiment and values below 4 indicate negative sentiment.

@@

As Definition~\ref{local} describes, for a user $ u $ in a global network, we can extract a $ \tau $-ego network $ G_{u}=\left( U,E_{u} \right)  $. 
Also the subjective model of each user $ u \in G_{u} $ can be concreted within the ego network. 
We denote tweets set published by a user $ u $ as $ M_{u}=\left\lbrace m_{i} \vert i \in \left[ 1, \cdots, N \right]  \right\rbrace$. All tweets in $ M_{u} $ is concatenated to a single document $ d_{u} $ to construct Local Topic Space $ T_{u}=\left\lbrace t_{i} \vert i=1, \cdots, K \right\rbrace $ with the LDA topic model.
The topic model is built with parameter $ \theta_{u} $\ representing the distribution of user $ u $ over topics he talks about, and parameter $ \beta_{k} $ represents the distribution of each topic over the vocabulary of all tweets. SentiStrength is applied to each tweet $ m $ in collection $ M_{u} $ and outputs sentiment strength $ s_{m} $ for tweet $ m $. 
Subjective model of user $ u $ is built as follows:
\begin{itemize}
\item Firstly, for user $ u $, the corresponding $ \theta_{u} $ can be regarded as his topic distribution in the Local Topic Space $ T_{u} $, and topics he cares about are $ Z_{u}= \left\lbrace z \vert p\left( z \vert \theta_{u}\left( z \right)  \right)>0 \right\rbrace $.
\item Secondly, in order to identify the target of opinion in each tweet, the topic model is applied to each tweet $ m $ to find topics it talks about, which are $ Z_{m} =\left\lbrace z_{m} \vert p\left( z_{m} \vert \theta, \beta, Z_{u} \right)>0 \right\rbrace $.
\item Thirdly, the opinion distribution of user $ u $ towards topic $ t \in Z_{u} $ could be calculated as: 
\begin{equation}
\label{opinionall}
d_{u,t}\left( o \right) = \left\lbrace \dfrac{N_{o}}{\sum_{o \in O} N_{o}} \vert O=\left[ 0, \cdots, 8 \right] \right\rbrace 
\end{equation}
where $ N_{o} $ is the number of times user $ u $ expresses an opinion towards topic $ t $ with sentiment strength $ o $, which could be calculated as:
\begin{equation}
\label{opinion1}
N_{o}=\sum_{m \in Mu} I\left( s_{m} \right) , \text{ if } s_{m}=o \& t \in Z_{m}
\end{equation}
\begin{equation}
\label{opinion2}
I\left( s_{m} \right)=\left\{
\begin{array}{ll}
{1} & \text{if } s_{m}=o \& t \in Z_{m}\\
{0} & \text{else}
\end{array}
\right.
\end{equation}
where $ s_{m} $ denotes the sentiment strength of tweet $ m $. For simplicity, we assume the sentiment of tweet $ m $ is related to every topic it talks about in $ Z_{m} $.
\end{itemize}

@@

Many factors have been proved to affect retweeting behavior \cite{Suh2010,conf/icwsm/MacskassyM11,Comarela:2012UFA}, however few researches have investigated the subjective motivation of a user to retweet a message. 
Therefore we will study whether the subjective model can help understand underlying reasons of a user's retweeting behavior.
Apart from the context constraints, a tweet is more likely to be retweeted by subjective users who find it worth to. 
Therefore, we are not interested in modelling the tweet by itself as other researches \cite{Naveed:2011SMC,2011:NaveedGKC,conf/icwsm/PfitznerGS12}, but how the tweet resonate with the users who might want to disseminate it. 
We assume the motivation of a user to retweet a message lies in that the user considers only the tweet content arousing his resonation without context perturbation. 
If a tweet is published, all followers of its author will receive it in time, and followers are likely to retweet it if they find it worthwhile. 
Under such assumption, we investigate the problem in a 1-ego network for the author of target tweets. 
The relation between tweet, author and followers can be illustrated as Figure~\ref{fig1}.
\begin{figure}[htb]
%\setlength{\belowcaptionskip}{-0.2cm} 
\centering
\includegraphics[width=2.1in,height=2.0in]{ego.pdf}
%\vspace{-4em}
\caption{Illustration of relations between tweet, author and followers. Author is denoted as $ u_{a} $, tweet as $ m $, followers as $ f_{i} $ and tweets of follower $ f_{i} $ as $ m_{i} $. An directed edge $ \left( f_{i},u_{a} \right)  $ means that $ f_{i} $ is exposed to the messages published by $ u_{a} $.}
\label{fig1}
\end{figure}

@@

The retweeting analysis problem can be formulated as follows:
For each target tweet $ m $, let $ F $ denotes the followers who receive $ m $ by following its author $ u_{a} $, and for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace  $, let $ M_{u} $ denotes   tweets the user has published. 
For each follower $ u_{f} \in F $, we can define a quadruple $ <u_{f}, u_{a}, m, r_{f}>  $: 
\begin{itemize}
\item $ r_{f} $ is a binary label indicating whether $ m $ is retweeted by $ u_{f} $.
\item Firstly our work focuses on building subjective model $ P\left( u \right)  $ for each user $ u \in F \cup \left\lbrace u_{a} \right\rbrace $ in the ego network with all tweets collections $ M=\left\lbrace M_{u} | u \in F \cup \left\lbrace u_{a} \right\rbrace  \right\rbrace  $.
\item Then we investigate the relation between the subjectivity of a user and his retweeting behavior to predict $ r_{f} $ by calculating subjective similarities between tweet $ m $, its author $ u_{a} $ and follower $ u_{f} $. 
\end{itemize}

@@

In order to understand the underlying reasons why a user retweets a message, we try to simulate the subjective decision-making procedure by investigating the relationship among a tweet and subjective models of its author and followers. 
We assume that if a tweet and the subjective models of a user are similar enough in terms of topics and opinions, the user will have a very high probability to retweet the tweet. 
We call this phenomenon as ``resonation'', and assume resonation between tweets and users will elicit retweeting behavior.
With subjective models built for users, we can define a similarity measurement to quantify the resonation among them.

@@

A topic distribution of a tweet can be obtained by applying the topic model estimated from the tweets collections of users.
The topic similarity between tweet and user can be calculated with methods such as the cosine distance \cite{cha2007comprehensive} or the Jensen-Shannon Divergence \cite{weng2010twitterrank} with satisfactory results.
In our research, we adopt a cosine distance to measure the topic similarity, which is defined as:
\begin{equation}
sim_{topic}=\dfrac{\theta_{m} \cdot \theta_{u}}{\parallel \theta_{m} \parallel \parallel \theta_{u} \parallel}
\end{equation}
where $ \theta_{u}$ denotes topic distribution of user $ u $ and $\theta_{m}$ denotes topic distribution of tweet $ m $.
